Constraining the Interiors of Asteroids Through Close Encounters

### 2022-03-26 paper/main.tex
Trying to figure out why the spin behaves so weirdly

>>>>

\jtd{To figure this out, I'm running some searches for spins along the equator. Hope to see the same peak at Y, and I'll see if it goes away for an iteration when gamma zero changes.}

\jtd{Tomorrow, I plan to do the rest of this paper and skip this section. If I can't figure it out, I'll remove it.}

\jtd{Remember to include the changes when a fast rotator comes in.}
